\mytitle

### 2016-09-27 pdocs/thesis/article-section-3.tex
charpy results tuning in article
demolisher results in article

\begin{figure}[htb!]
\centering
\includegraphics[height=8cm]{figs/article-charpy}
\caption{Simulation of Charpy impact test}
\label{fig:f1-ok-results}
\end{figure}

>>>>

Figure \ref{fig:charpy} shows screenshot from simulation.
\begin{figure}[htb!]
\centering
\includegraphics[height=8cm]{figs/article-charpy}
\caption{Simulation of Charpy impact test}
\label{fig:charpy}
\end{figure}

\subsection{Demolisher}
Demolisher is  collection of possible scenarios that can be added to games to provide ductile joints between
rigid bodies.  Simulation can be done in real time on modest hardware. 
Figure \ref{fig:demolisher} shows three screenshots from simulation.

\begin{figure}[htb!]
\centering
\includegraphics[height=5cm]{figs/demolisher-pre}
\includegraphics[height=5cm]{figs/demolisher-wip}
\includegraphics[height=5cm]{figs/demolisher-done}
\caption{Simulation of Demolisher scenario}
\label{fig:demolisher}
\end{figure}

Vehicle is modelled as single box btRaycastVehicle with four driving wheels. Wheels are rendered for visual feedback.
In left picture, initial state is shown. Gate in front is modelled to be so slender that it has visible elastic deflection.
Gate support is modelled as heavy box.
Bridge has rigid ramps and supports at both ends.
Gravity is applied gradually to avoid collapse of bridge at start of simulation.
In middle picture,  bridge is shown in state where car hs driven once over bridge without stopping and
other bodies have taken light damage.
In right picture, some of joints have been broken.
